Model-Based CubeSat Flight-Software Architecture using a Docs-as-Code Approach

### 2022-12-10 manuscript.tex
deploy: a4a77b6eaea83c04292b9bfae15b400f03ddbec3

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.5\textwidth]{swartwout_data_graph}
    \caption{Nanosatellite launch data provided by M. Swartwout \cite{swartwout_data}.}
    \label{swartwout_data_graph}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.5\textwidth]{ping_satellite}
    \caption{An example YAML file for a user story.}
    \label{user_story}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.5\textwidth]{stakeholder-needs-mapping}
    \caption{a view describing a mapping of stakeholders to stakeholder needs as a UML diagram}
    \label{stakeholder-needs-mapping}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.5\textwidth]{user-stories-mapping}
    \caption{a view describing a mapping of stakeholder needs to their derived user stories as a UML diagram}
    \label{user-stories-mapping}
\end{figure}

@@

An example data structure can be derived from user stories as presented in figure \ref{data-structures-mapping}.

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.5\textwidth]{data-structures-mapping}
    \caption{a view describing a mapping of user stories to their derived data structures as a UML diagram}
    \label{data-structures-mapping}
\end{figure}

>>>>

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.8\textwidth]{swartwout_data_graph}
    \caption{Nanosatellite launch data provided by M. Swartwout \cite{swartwout_data}.}
    \label{swartwout_data_graph}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.8\textwidth]{ping_satellite}
    \caption{An example YAML file for a user story.}
    \label{user_story}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.8\textwidth]{stakeholder-needs-mapping}
    \caption{a view describing a mapping of stakeholders to stakeholder needs as a UML diagram}
    \label{stakeholder-needs-mapping}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.8\textwidth]{user-stories-mapping}
    \caption{a view describing a mapping of stakeholder needs to their derived user stories as a UML diagram}
    \label{user-stories-mapping}
\end{figure}

Alternative views can also be rendered from a model. For example, the user stories can also be rendered as a use case diagram \ref{use-case-diagram}.
\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.8\textwidth]{use-case-diagram}
    \caption{a view describing user stories as a usecase diagram}
    \label{use-case-diagram}
\end{figure}

@@

A colletion of data structures can be derived from user stories as presented in figure \ref{data-structures-mapping}.

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=.8\textwidth]{data-structures-mapping}
    \caption{a view describing a mapping of user stories to their derived data structures as a UML diagram}
    \label{data-structures-mapping}
\end{figure}

Because models are both human and machine readable, thus, a specification document can also be generated. For example, the following is a table rendering of the data structure of the satellite health data packet:

\begin{center}
\include{satellite-health-data-packet-as-table}
\end{center}

This manuscript document itself was also modeled and generated using the m30ml modeling language and toolchain.
